Scheduling and Parallelization for MPC

### 2019-12-27 paper.tex
Changes.

% Used for Theorems and Definitions
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{remark}{Remark}

@@

@@

\end{tabular}
\caption{(a) shows the source code, taken from Aiken and Nicolau~\cite{Aiken:1988}, 
(b) shows the dependence graph. The solid edges denote within-iteration ordering constraints, e.g., A must run before B
because B depends on A. The dashed edges denote across-iteration ordering constraints, e.g., B(2), i.e., B in iteration 2
depends on D(1), i.e., D in iteration 1. (c) shows the optimal loop-body schedule, and (d) shows the
optimal across-loop schedule. A(1), B(1), etc. denote instruction A in iteration 1, etc.}
\label{fig:MPCexample}\vspace{-2ex}
\end{figure*}

@@

>>>>

% Used for Theorems and Definitions
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}

@@

\ana{Scope of paper: Should we expand towards 1) nested loops, 2) conversions, 3) implementation (what will we be saying with an implementation?)}

@@

\end{tabular}
\caption{(a) shows the source code, taken from Aiken and Nicolau~\cite{Aiken:1988}, 
(b) shows the dependence graph. The solid edges denote within-iteration ordering constraints, e.g., A must run before B
because B depends on A. The dashed edges denote across-iteration ordering constraints, e.g., B(2), i.e., B in iteration 2
depends on D(1), i.e., D in iteration 1; in the HPC literature these are known as loop-carried dependencies. 
(c) shows the optimal loop-body schedule, and (d) shows the optimal across-loop schedule. A(1), B(1), etc. denote 
instruction A in iteration 1, etc.}
\label{fig:MPCexample}\vspace{-2ex}
\end{figure*}

@@

The ``constant rate'' assumption states that a statement $A$ depends on 
itself at a ``constant rate'', i.e., there cannot be a case where $A(i)$ depends 
on $A(j), j<i$ and on $A(k), k<i$ s.t. $i \neq j$. \ana{Why the constant rate assumption?}

\begin{assumption} Let $A(j) \dashrightarrow \cdot \longrightarrow A(i)$ be a dependence chain,
where the dashed arrow denotes the loop carried dependence. For every 
$A(j) \dashrightarrow \cdot \longrightarrow A(i)$ we have $i = j+m$ for some constant $m$.
\end{assumption}
